{\fontfamily{ptm}\selectfont Lorum ipsum}

### 2025-07-03 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w<, start of the day changes

            Let $(\alpha_k)_{k \ge 0}$ be a sequence such that $\alpha_0 \in (0, 1]$ and, for all $k \ge 1$, it's recursively satisfies equality: 

@@

>>>>

            Let $(\alpha_k)_{k \ge 0}$ be a sequence such that $\alpha_0 \in (0, 1]$ and, for all $k \ge 1$, it satisfies recursively the equality: 

@@

            Let $\mathbb E_k$ denotes the expectation conditioned on $I_0, I_1, \ldots, I_{k - 1}$. 
